% Pandoc LaTeX template for checklists with basic PDF forms
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amssymb}
% Optional AcroTeX eForms for richer widgets
\usepackage{eforms}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\usepackage{enumitem}
\setlist[itemize]{left=1.2em}
\setlist{noitemsep}
\def\tightlist{}

% Abstraction layer for form widgets
  % eForms uses \checkBox and \textField
  \newcommand{\mkCheckBox}[2][]{\checkBox[#1]{#2}}
  \newcommand{\mkTextField}[2][]{\textField[#1]{#2}}

% Enable form environment for interactive fields
% Usage in content requires raw LaTeX or a pandoc Lua filter to insert \CheckBox/\TextField
\begin{document}

\begin{center}
{\LARGE }\\[4pt]
\normalsize 
\end{center}
\vspace{1em}

% Begin PDF form region
\begin{Form}

\section{MOOSE Checklist}\label{moose-checklist}

\begin{quote}
Scope: Meta-analysis Of Observational Studies in Epidemiology.

Reference: See \texttt{source/archetypes/moose-2000.yml} for canonical
link and provenance.
\end{quote}

\subsection{Instructions}\label{instructions}

\begin{itemize}
\tightlist
\item
  Use the boxes to confirm each reporting item.
\item
  Add reviewer notes under each section as needed.
\end{itemize}

\subsection{Reporting of Background}\label{reporting-of-background}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{1. Problem definition:} Clearly state the research question.
\item[$\square$]
  \textbf{2. Hypothesis:} State the hypothesis being tested.
\item[$\square$]
  \textbf{3. Study objectives:} Describe the study objectives.
\item[$\square$]
  \textbf{4. Rationale:} Provide the rationale for the review in the
  context of what is already known.
\end{itemize}

\subsection{Reporting of Search
Strategy}\label{reporting-of-search-strategy}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{5. Search criteria:} Specify the inclusion and exclusion
  criteria for the review.
\item[$\square$]
  \textbf{6. Information sources:} Specify all information sources used
  to identify studies, including databases, registers, and other
  sources.
\item[$\square$]
  \textbf{7. Search terms:} Describe the search strategy, including
  search terms and any limits used.
\item[$\square$]
  \textbf{8. Search process:} Describe the process for selecting studies
  for inclusion in the review.
\end{itemize}

\subsection{Reporting of Methods}\label{reporting-of-methods}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{9. Data extraction:} Describe the methods used to extract data
  from reports, including how many reviewers extracted data and whether
  they worked independently.
\item[$\square$]
  \textbf{10. Data items:} List and define all variables for which data
  were sought.
\item[$\square$]
  \textbf{11. Study quality assessment:} Describe the methods used to
  assess the quality of the included studies.
\item[$\square$]
  \textbf{12. Data synthesis:} Describe the methods of data synthesis,
  including the summary measures and any investigation of heterogeneity.
\item[$\square$]
  \textbf{13. Publication bias:} Describe any methods used to assess
  publication bias.
\end{itemize}

\subsection{Reporting of Results}\label{reporting-of-results}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{14. Study selection:} Describe the results of the study
  selection process, including the number of studies included in the
  review.
\item[$\square$]
  \textbf{15. Study characteristics:} Present the characteristics of the
  included studies.
\item[$\square$]
  \textbf{16. Quantitative data synthesis:} Present the results of the
  data synthesis, including the summary measures and any investigation
  of heterogeneity.
\item[$\square$]
  \textbf{17. Publication bias:} Present the results of any assessment
  of publication bias.
\end{itemize}

\subsection{Reporting of Discussion}\label{reporting-of-discussion}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{18. Summary of evidence:} Summarize the main findings and
  their strength.
\item[$\square$]
  \textbf{19. Limitations:} Discuss the limitations of the review.
\item[$\square$]
  \textbf{20. Conclusions:} Provide a general interpretation of the
  results and their implications.
\end{itemize}

\subsection{Reporting of Funding}\label{reporting-of-funding}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{21. Funding:} Describe the sources of funding for the review.
\end{itemize}

\subsubsection{Notes}\label{notes}

{Reviewer notes}

\subsection{Provenance}\label{provenance}

\begin{itemize}
\tightlist
\item
  Source: See sidecar metadata in
  \texttt{source/archetypes/moose-2000.yml}
\item
  Version: 2000
\item
  License: TBD
\end{itemize}

\end{Form}

\end{document}
