% Pandoc LaTeX template for checklists with basic PDF forms
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amssymb}
% Optional AcroTeX eForms for richer widgets
\usepackage{eforms}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\usepackage{enumitem}
\setlist[itemize]{left=1.2em}
\setlist{noitemsep}
\def\tightlist{}

% Abstraction layer for form widgets
  % eForms uses \checkBox and \textField
  \newcommand{\mkCheckBox}[2][]{\checkBox[#1]{#2}}
  \newcommand{\mkTextField}[2][]{\textField[#1]{#2}}

% Enable form environment for interactive fields
% Usage in content requires raw LaTeX or a pandoc Lua filter to insert \CheckBox/\TextField
\begin{document}

\begin{center}
{\LARGE }\\[4pt]
\normalsize 
\end{center}
\vspace{1em}

% Begin PDF form region
\begin{Form}

\section{TRIPOD 2015 Checklist}\label{tripod-2015-checklist}

\begin{quote}
Scope: The Transparent Reporting of a multivariable prediction model for
Individual Prognosis Or Diagnosis (TRIPOD) Statement was developed to
improve the quality of reporting in studies that develop, validate, or
update prediction models.

Reference: See \texttt{source/archetypes/tripod-2015.yml} for canonical
link and provenance.
\end{quote}

\subsection{Instructions}\label{instructions}

\begin{itemize}
\tightlist
\item
  Use task list items for checklist boxes; these become interactive
  checkboxes in PDF.
\item
  Use a span with class \texttt{.textfield} for free‑text fields.
\end{itemize}

\subsection{Title and Abstract}\label{title-and-abstract}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{1. Title:} Identify the study as one that develops, validates,
  or updates a multivariable prediction model, specify the target
  population, and the outcome to be predicted.
\item[$\square$]
  \textbf{2. Abstract:} Provide a summary of the objectives, study
  design, setting, participants, sample size, predictors, outcome,
  statistical analysis, results, and conclusions.
\end{itemize}

\subsection{Introduction}\label{introduction}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{3. Background and Objectives:} Explain the medical context and
  rationale for the study, including references to existing models.
\end{itemize}

\subsection{Methods}\label{methods}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{4. Source of data:} Describe the study design and key elements
  of the study setting.
\item[$\square$]
  \textbf{5. Participants:} Describe the eligibility criteria for
  participants.
\item[$\square$]
  \textbf{6. Outcome:} Clearly define the outcome that is predicted by
  the model, including how and when it was assessed.
\item[$\square$]
  \textbf{7. Predictors:} Clearly define all predictors used in the
  model, including how and when they were measured.
\item[$\square$]
  \textbf{8. Sample size:} Explain how the study size was determined.
\item[$\square$]
  \textbf{9. Missing data:} Describe how missing data were handled.
\item[$\square$]
  \textbf{10. Statistical analysis methods:} Describe how predictors
  were handled in the analyses.
\item[$\square$]
  \textbf{11. Model development:} Specify the type of model, all
  model-building procedures, and the method for internal validation.
\item[$\square$]
  \textbf{12. Model performance:} Specify all measures used to assess
  model performance and, if relevant, to compare multiple models.
\end{itemize}

\subsection{Results}\label{results}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{13. Participants:} Describe the flow of participants through
  the study.
\item[$\square$]
  \textbf{14. Model development:} Specify the number of participants and
  outcome events in each analysis.
\item[$\square$]
  \textbf{15. Model specification:} Present the full prediction model
  for use by others.
\item[$\square$]
  \textbf{16. Model performance:} Report performance measures for the
  prediction model.
\item[$\square$]
  \textbf{17. Model validation:} For validation, describe how the
  predictions were calculated and report the results.
\end{itemize}

\subsection{Discussion}\label{discussion}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{18. Limitations:} Discuss any limitations of the study.
\item[$\square$]
  \textbf{19. Interpretation:} Give an overall interpretation of the
  results, considering objectives, limitations, and other relevant
  evidence.
\item[$\square$]
  \textbf{20. Implications:} Discuss the implications for practice and
  research.
\end{itemize}

\subsection{Other Information}\label{other-information}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{21. Supplementary information:} Provide information about the
  availability of supplementary resources.
\item[$\square$]
  \textbf{22. Funding:} Disclose the source of funding and the role of
  the funders.
\end{itemize}

{Notes}

\subsection{Provenance}\label{provenance}

\begin{itemize}
\tightlist
\item
  Source: See sidecar metadata in
  \texttt{source/archetypes/tripod-2015.yml}
\item
  Version: 2015
\item
  License: Custom; see website
\end{itemize}

\end{Form}

\end{document}
