% Pandoc LaTeX template for checklists with basic PDF forms
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amssymb}
% Optional AcroTeX eForms for richer widgets
\usepackage{eforms}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\usepackage{enumitem}
\setlist[itemize]{left=1.2em}
\setlist{noitemsep}
\def\tightlist{}

% Abstraction layer for form widgets
  % eForms uses \checkBox and \textField
  \newcommand{\mkCheckBox}[2][]{\checkBox[#1]{#2}}
  \newcommand{\mkTextField}[2][]{\textField[#1]{#2}}

% Enable form environment for interactive fields
% Usage in content requires raw LaTeX or a pandoc Lua filter to insert \CheckBox/\TextField
\begin{document}

\begin{center}
{\LARGE CONSORT for Abstracts}\\[4pt]
\normalsize Date: 2008-04-22
\end{center}
\vspace{1em}

% Begin PDF form region
\begin{Form}

\section{CONSORT for Abstracts
Checklist}\label{consort-for-abstracts-checklist}

\begin{quote}
Scope: Preferred Reporting Items for reporting randomized controlled
trials in journal and conference abstracts.

Reference: See \texttt{source/variants/consort-abstracts.yml} for
canonical link and provenance.
\end{quote}

\subsection{Instructions}\label{instructions}

\begin{itemize}
\tightlist
\item
  Use the boxes to confirm each reporting item.
\item
  Add reviewer notes under each section as needed.
\end{itemize}

\subsection{Checklist Items}\label{checklist-items}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{Title:} Identification of the study as a randomized trial.
\item[$\square$]
  \textbf{Authors:} Contact details for the corresponding author.
\item[$\square$]
  \textbf{Trial design:} Description of the trial design (e.g.,
  parallel, cluster, non-inferiority).
\item[$\square$]
  \textbf{Methods:}

  \begin{itemize}
  \tightlist
  \item[$\square$]
    \textbf{Participants:} Eligibility criteria for participants and the
    settings where the data were collected.
  \item[$\square$]
    \textbf{Interventions:} Interventions intended for each group.
  \item[$\square$]
    \textbf{Objective:} Specific objective or hypothesis.
  \item[$\square$]
    \textbf{Outcomes:} Clearly defined primary outcome for this report.
  \item[$\square$]
    \textbf{Randomization:} How participants were allocated to
    interventions.
  \item[$\square$]
    \textbf{Blinding (masking):} Whether or not participants, care
    givers, and those assessing the outcomes were blinded to group
    assignment.
  \end{itemize}
\item[$\square$]
  \textbf{Results:}

  \begin{itemize}
  \tightlist
  \item[$\square$]
    \textbf{Numbers randomized:} Number of participants randomized to
    each group.
  \item[$\square$]
    \textbf{Recruitment:} Trial status.
  \item[$\square$]
    \textbf{Numbers analyzed:} Number of participants analyzed in each
    group.
  \item[$\square$]
    \textbf{Outcome:} For the primary outcome, a result for each group
    and the estimated effect size and its precision.
  \item[$\square$]
    \textbf{Harms:} Important adverse events or side effects.
  \end{itemize}
\item[$\square$]
  \textbf{Conclusions:} General interpretation of the results.
\item[$\square$]
  \textbf{Trial registration:} Registration number and name of trial
  register.
\item[$\square$]
  \textbf{Funding:} Source of funding.
\end{itemize}

\subsubsection{Notes}\label{notes}

{Reviewer notes}

\end{Form}

\end{document}
