% Pandoc LaTeX template for checklists with basic PDF forms
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amssymb}
% Optional AcroTeX eForms for richer widgets
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\usepackage{enumitem}
\setlist[itemize]{left=1.2em}
\setlist{noitemsep}
\def\tightlist{}

% Abstraction layer for form widgets
  % hyperref provides \CheckBox and \TextField
  \newcommand{\mkCheckBox}[2][]{\CheckBox[#1]{#2}}
  \newcommand{\mkTextField}[2][]{\TextField[#1]{#2}}

% Enable form environment for interactive fields
% Usage in content requires raw LaTeX or a pandoc Lua filter to insert \CheckBox/\TextField
\begin{document}

\begin{center}
{\LARGE }\\[4pt]
\normalsize 
\end{center}
\vspace{1em}

% Begin PDF form region
\begin{Form}

\section{COREQ Checklist}\label{coreq-checklist}

\begin{quote}
Scope: COnsolidated criteria for REporting Qualitative research.

Reference: See \texttt{source/archetypes/coreq-2007.yml} for canonical
link and provenance.
\end{quote}

\subsection{Instructions}\label{instructions}

\begin{itemize}
\tightlist
\item
  Use the boxes to confirm each reporting item.
\item
  Add reviewer notes under each section as needed.
\end{itemize}

\subsection{Domain 1: Research team and
reflexivity}\label{domain-1-research-team-and-reflexivity}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{1. Interviewer/facilitator:} Which author/s conducted the
  interview/focus group?
\item[$\square$]
  \textbf{2. Credentials:} What were the researcher's credentials? E.g.
  PhD, MD.
\item[$\square$]
  \textbf{3. Occupation:} What was their occupation at the time of the
  study?
\item[$\square$]
  \textbf{4. Gender:} Was the researcher male or female?
\item[$\square$]
  \textbf{5. Experience and training:} What experience or training did
  the researcher have?
\item[$\square$]
  \textbf{6. Relationship established:} Was a relationship established
  prior to study commencement?
\item[$\square$]
  \textbf{7. Participant knowledge of the interviewer:} What did the
  participants know about the researcher? e.g.~personal goals, reasons
  for doing the research.
\item[$\square$]
  \textbf{8. Interviewer characteristics:} What were the interviewer's
  characteristics? e.g.~assumptions, reasons for doing the research,
  relationship with participants.
\end{itemize}

\subsection{Domain 2: Study design}\label{domain-2-study-design}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{9. Methodological orientation and theory:} What is the
  methodological orientation and what is the theoretical framework for
  the study?
\item[$\square$]
  \textbf{10. Sampling:} How were participants selected? e.g.~purposive,
  convenience, consecutive, snowball.
\item[$\square$]
  \textbf{11. Method of approach:} How were participants approached?
  e.g.~face-to-face, telephone, mail, email.
\item[$\square$]
  \textbf{12. Sample size:} How many participants were in the study?
\item[$\square$]
  \textbf{13. Non-participation:} How many people refused to participate
  or dropped out? Reasons?
\item[$\square$]
  \textbf{14. Setting of data collection:} Where was the data collected?
  e.g.~home, clinic, workplace.
\item[$\square$]
  \textbf{15. Presence of non-participants:} Was anyone else present
  besides the participants and researchers?
\item[$\square$]
  \textbf{16. Description of sample:} What were the important
  characteristics of the sample? e.g.~demographic data, date.
\end{itemize}

\subsection{Domain 3: Analysis and
findings}\label{domain-3-analysis-and-findings}

\begin{itemize}
\tightlist
\item[$\square$]
  \textbf{17. Data analysis:} How many data coders coded the data?
\item[$\square$]
  \textbf{18. Derivation of themes:} Were themes identified in advance
  or did they emerge from the data?
\item[$\square$]
  \textbf{19. Software:} What software, if applicable, was used to
  manage the data?
\item[$\square$]
  \textbf{20. Participant checking:} Did participants provide feedback
  on the findings?
\item[$\square$]
  \textbf{21. Major themes:} Were major themes clearly presented in the
  findings?
\item[$\square$]
  \textbf{22. Clarity of themes:} Is there a description of how themes
  were developed?
\item[$\square$]
  \textbf{23. Quotations presented:} Were quotations presented to
  illustrate the themes?
\item[$\square$]
  \textbf{24. Data and findings consistent:} Was there consistency
  between the data presented and the findings?
\item[$\square$]
  \textbf{25. Clarity of major themes:} Were major themes clearly
  presented in the findings?
\item[$\square$]
  \textbf{26. Clarity of minor themes:} Were minor themes clearly
  presented in the findings?
\end{itemize}

\subsubsection{Notes}\label{notes}

{Reviewer notes}

\subsection{Provenance}\label{provenance}

\begin{itemize}
\tightlist
\item
  Source: See sidecar metadata in
  \texttt{source/archetypes/coreq-2007.yml}
\item
  Version: 2007
\item
  License: All Rights Reserved
\end{itemize}

\end{Form}

\end{document}
